---
title: "Name Of Project"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed
    orientation: rows
    social: [ "menu" ]
    vertical_layout: scroll
    theme: bootstrap
---



```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(DT)
library(dygraphs)
```

# Introduction {data-icon="fa-home"}

In this field you will see an introductory text to this open-data website

* A
* B
* C


Create your own open-data websites by looking at our source-code in the top right corner.

# Method {data-orientation=columns}

### Method Description

Test ABS

* A
* B
* C

Links can be included as well
[Google](http://www.google.com)

Method Figures
-----------


### Method 1

Aha
```{r}
p <- ggplot(cars) + aes(x = speed, y = dist) + geom_point()
ggplotly(p)
```

### Method 2

```{r}
p <- ggplot(cars) + aes(x = speed, y = dist) + geom_point()
ggplotly(p)
```






# Results

Row 
-------------------------------------

### Chart 1
```{r}

```


Row {.tabset .tabset-fade}
-------------------------------------
   
### Chart 2

```{r}
```   
 
### Chart 3
    
```{r}
```


Row
-------------------------------------

### Test 123

# Discussion
### Chart 1
```{r}
dygraph(cars)
```

# Data 


Row {.tabset .tabset-fade}
-------------------------------------

### Data: mpg {data-height=800}

```{r}
datatable(mpg, filter = list(position = 'top', clear = TRUE, plain = FALSE), extensions = c('Buttons','FixedColumns'), options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf'),
    scrollX = TRUE,
    fixedColumns = TRUE
  ))
```   
 
### Data: other
    
```{r}
```




# Sidebar {.sidebar}

**Welcome**

Here we have general text that can help you orient yourself.

* You may share a link to this website using the share button in the top right corner.
* The [Data] page contains a table browser for each dataset used in this study. You may also download the data as *CSV* or *Excel* files for your own analysis.


